### 2018-03-07 acknowledge.tex
Consolidate acknoledgements

%Chapter 2 Stuff
We thank Ryan Chornock, Maria Drout, Wen-fai Fong, Ryan Foley, Daniel Kasen, Brian Metzger, Armin Rest, and Ken Shen for helpful discussions and providing model data during the course of this analysis. P.S.C. is grateful for support provided by the NSF through the Graduate Research Fellowship Program, grant DGE1144152.

%Chapter 3 Stuff
The Berger Time-Domain Group at Harvard is supported in part by the NSF through grants AST-1411763 and AST-1714498, and by NASA through grants NNX15AE50G and NNX16AC22G. P.S.C. is grateful for support provided by the NSF
through the Graduate Research Fellowship Program, grant DGE1144152. The UCSC group is supported in part by NSF grant AST--1518052, the Gordon \& Betty Moore Foundation, and from fellowships from the Alfred P.\ Sloan Foundation and the David and Lucile Packard Foundation to R.J.F.

This work has made use of data from the European Space Agency (ESA)
mission \gaia (\url{https://www.cosmos.esa.int/gaia}), processed by
the \gaia Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the \gaia Multilateral Agreement.
This publication makes use of data products from the Two Micron All Sky Survey,
which is a joint project of the University of Massachusetts and the Infrared Processing
and Analysis Center/California Institute of Technology, funded by the National Aeronautics
and Space Administration and the National Science Foundation. This publication makes use
of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the
University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of
Technology, funded by the National Aeronautics and Space Administration.

% Chapter 4 Stuff
P.S.C. is grateful for support provided by the NSF
through the Graduate Research Fellowship Program, grant DGE1144152.
R.J.F.\ gratefully acknowledges support from NSF grant AST--1518052 and
the Alfred P.\ Sloan Foundation. D.E.H.\ was supported by NSF CAREER grant
PHY-1151836. He also acknowledges support from the Kavli Institute for
Cosmological Physics at the University of Chicago through NSF grant
PHY-1125897 as well as an endowment from the Kavli Foundation.

This research uses services or data provided by the NOAO Science
Archive. NOAO is operated by the Association of Universities for
Research in Astronomy (AURA), Inc. under a cooperative agreement with
the National Science Foundation. The computations in this paper were
run on the Odyssey cluster supported by the FAS Division of Science,
Research Computing Group at Harvard University. This research has made
use of the NASA/IPAC Extragalactic Database (NED) which is operated by
the Jet Propulsion Laboratory, California Institute of Technology,
under contract with the National Aeronautics and Space Administration.
Light curve data for PS15cdi were obtained from The Open Supernova
Catalog \citep{Guillochon+17}. Some of the results in this paper have been
derived using the HEALPix package \citep{Gorski+05}.

Funding for the DES Projects has been provided by the DOE and NSF (USA),
MEC/MICINN/ MINECO (Spain), STFC (UK), HEFCE (UK). NCSA (UIUC),
KICP (U. Chicago), CCAPP (Ohio State), MIFPA (Texas A\&M), CNPQ, FAPERJ,
FINEP (Brazil), DFG (Germany) and the Collaborating Institutions in the Dark Energy Survey.

The Collaborating Institutions are Argonne Lab, UC Santa Cruz,
University of Cambridge, CIEMAT-Madrid, University of Chicago, University College London,
DES-Brazil Consortium, University of Edinburgh, ETH Z{\"u}rich, Fermilab,
University of Illinois, ICE (IEEC-CSIC), IFAE Barcelona, Lawrence Berkeley Lab,
LMU M{\"u}nchen and the associated Excellence Cluster Universe,
University of Michigan, NOAO, University of Nottingham, Ohio State University, University of
Pennsylvania, University of Portsmouth, SLAC National Lab, Stanford University,
University of Sussex, Texas A\&M University, and the OzDES Membership Consortium.

@@

% Chapter 5
The Berger Time-Domain Group at Harvard is supported in part by the NSF through grants AST-1411763 and AST-1714498, and by NASA through grants NNX15AE50G and NNX16AC22G. PSC is grateful for support provided by the NSF through the Graduate Research Fellowship Program, grant DGE 1144152. VAV acknowledges support by the National Science Foundation through a Graduate Research Fellowship. DAB is supposed by NSF award PHY-1707954. We thank the University of Copenhagen, DARK Cosmology Centre, and the Niels Bohr International Academy for hosting R.J.F.\ during the discovery of GW170817/SSS17a, where he was participating in the Kavli Summer Program in Astrophysics, ``Astrophysics with gravitational wave detections."  This program was supported by the Kavli Foundation, Danish National Research Foundation, the Niels Bohr International Academy, and the DARK Cosmology Centre. The UCSC group is supported in part by NSF grant AST--1518052, the Gordon \& Betty Moore Foundation, the Heising-Simons Foundation, generous donations from many individuals through a UCSC Giving Day grant, and from fellowships from the Alfred P.\ Sloan Foundation and the David and Lucile Packard Foundation to R.J.F. EB acknowledges financial support from the European Research Council (ERC-StG-335936, CLUSTERS). DK \& EQ were funded in part by the Gordon and Betty Moore Foundation through Grant GBMF5076.

We are grateful for the heroic efforts of the entire staff at Gemini-South to continue obtaining observations of this target in evening twilight at high airmass as the object was setting.

This project used data obtained with the Dark Energy Camera (DECam), which was constructed by the Dark Energy Survey (DES) collaboration. Funding for the DES Projects has been provided by the DOE and NSF (USA), MISE (Spain), STFC (UK), HEFCE (UK), NCSA (UIUC), KICP (U. Chicago), CCAPP (Ohio State), MIFPA (Texas A\&M), CNPQ, FAPERJ, FINEP (Brazil), MINECO (Spain), DFG (Germany) and the collaborating institutions in the Dark Energy Survey, which are Argonne Lab, UC Santa Cruz, University of Cambridge, CIEMAT-Madrid, University of Chicago, University College London, DES-Brazil Consortium, University of Edinburgh, ETH Z{\"u}rich, Fermilab, University of Illinois, ICE (IEEC-CSIC), IFAE Barcelona, Lawrence Berkeley Lab, LMU M{\"u}nchen and the associated Excellence Cluster Universe, University of Michigan, NOAO, University of Nottingham, Ohio State University, University of Pennsylvania, University of Portsmouth, SLAC National Lab, Stanford University, University of Sussex, and Texas A\&M University.

Based in part on observations at Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory (NOAO Prop. ID: 2017B-0110, PI: E. Berger), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation

Based in part on observations obtained at the Gemini Observatory (Program IDs GS-2017B-Q-8 and GS-2017B-DD-4; PI: Chornock), which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).

>>>>

Graduate advisor

Undergraduate advisors

Research Group and Collaborators

Grad School Palmese

Family and Friends

The Berger Time-Domain Group at Harvard is supported in part by the NSF through grants AST-1411763 and AST-1714498, and by NASA through grants NNX15AE50G and NNX16AC22G. P.S.C. is grateful for support provided by the NSF through the Graduate Research Fellowship Program, grant DGE1144152. V.A.V. acknowledges support by the National Science Foundation through a Graduate Research Fellowship. EB acknowledges financial support from the European Research Council (ERC-StG-335936, CLUSTERS). DK \& EQ were funded in part by the Gordon and Betty Moore Foundation through Grant GBMF5076. DAB is supposed by NSF award PHY-1707954.

The UCSC group is supported in part by NSF grant AST--1518052, the Gordon \& Betty Moore Foundation, the Heising-Simons Foundation, generous donations from many individuals through a UCSC Giving Day grant, and from fellowships from the Alfred P.\ Sloan Foundation and the David and Lucile Packard Foundation to R.J.F. R.J.F.\ gratefully acknowledges support from NSF grant AST--1518052 and the Alfred P.\ Sloan Foundation. D.E.H.\ was supported by NSF CAREER grant PHY-1151836. He also acknowledges support from the Kavli Institute for Cosmological Physics at the University of Chicago through NSF grant PHY-1125897 as well as an endowment from the Kavli Foundation.

R.J.F.\ thanks the University of Copenhagen, DARK Cosmology Centre, and the Niels Bohr International Academy for hosting during the discovery of GW170817/SSS17a, where he was participating in the Kavli Summer Program in Astrophysics, ``Astrophysics with gravitational wave detections."  This program was supported by the Kavli Foundation, Danish National Research Foundation, the Niels Bohr International Academy, and the DARK Cosmology Centre.

This thesis uses services or data provided by the NOAO Science Archive. NOAO is operated by the Association of Universities for Research in Astronomy (AURA), Inc. under a cooperative agreement with the National Science Foundation. The computations in this thesis were run on the Odyssey cluster supported by the FAS Division of Science, Research Computing Group at Harvard University. This thesis has made use of the NASA/IPAC Extragalactic Database (NED) which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. Some of the results in this thesis have been derived using the HEALPix package \citep{Gorski+05}.

The work presented in Chapter 2 relied upon Ryan Chornock, Maria Drout, Wen-fai Fong, Ryan Foley, Daniel Kasen, Brian Metzger, Armin Rest, and Ken Shen for helpful discussions and providing model data during the course of the analysis.

This thesis has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia Multilateral Agreement. This thesis makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation. This thesis makes use of data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and the Jet Propulsion Laboratory/California Institute of Technology, funded by the National Aeronautics and Space Administration.

The light curve data for PS15cdi used in Chapter 4 were obtained from The Open Supernova
Catalog \citep{Guillochon+17}.

This thesis used data obtained with the Dark Energy Camera (DECam), which was constructed by the Dark Energy Survey (DES) collaboration. Funding for the DES Projects has been provided by the U.S. Department of Energy, the U.S. National Science Foundation, the Ministry of Science and Education of Spain, the Science and Technology FacilitiesCouncil of the United Kingdom, the Higher Education Funding Council for England, the National Center for Supercomputing Applications at the University of Illinois at Urbana-Champaign, the Kavli Institute of Cosmological Physics at the University of Chicago, the Center for Cosmology and Astro-Particle Physics at the Ohio State University, the Mitchell Institute for Fundamental Physics and Astronomy at Texas A\&M University, Financiadora de Estudos e Projetos, Funda{\c c}{\~a}o Carlos Chagas Filho de Amparo {\`a} Pesquisa do Estado do Rio de Janeiro, Conselho Nacional de Desenvolvimento Cient{\'i}fico e Tecnol{\'o}gico and the Minist{\'e}rio da Ci{\^e}ncia, Tecnologia e Inova{\c c}{\~a}o, the Deutsche Forschungsgemeinschaft, and the Collaborating Institutions in the Dark Energy Survey.

The Collaborating Institutions are Argonne National Laboratory, the University of California at Santa Cruz, the University of Cambridge, Centro de Investigaciones Energ{\'e}ticas, Medioambientales y Tecnol{\'o}gicas-Madrid, the University of Chicago, University College London, the DES-Brazil Consortium, the University of Edinburgh, the Eidgen{\"o}ssische Technische Hochschule (ETH) Z{\"u}rich,  Fermi National Accelerator Laboratory, the University of Illinois at Urbana-Champaign, the Institut de Ci{\`e}ncies de l'Espai (IEEC/CSIC), the Institut de F{\'i}sica d'Altes Energies, Lawrence Berkeley National Laboratory, the Ludwig-Maximilians Universit{\"a}t M{\"u}nchen and the associated Excellence Cluster Universe, the University of Michigan, the National Optical Astronomy Observatory, the University of Nottingham, The Ohio State University, the OzDES Membership Consortium, the University of Pennsylvania, the University of Portsmouth, SLAC National Accelerator Laboratory, Stanford University, the University of Sussex, and Texas A\&M University.

@@

This thesis is based in part on observations at Cerro Tololo Inter-American Observatory, National Optical Astronomy Observatory (NOAO Prop. ID: 2017B-0110, PI: E. Berger), which is operated by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation

This thesis is based in part on observations obtained at the Gemini Observatory (Program IDs GS-2017B-Q-8 and GS-2017B-DD-4; PI: Chornock), which is operated by the Association of Universities for Research in Astronomy, Inc., under a cooperative agreement with the NSF on behalf of the Gemini partnership: the National Science Foundation (United States), the National Research Council (Canada), CONICYT (Chile), Ministerio de Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina), and Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil).

We are grateful for the heroic efforts of the entire staff at Gemini-South to continue obtaining observations of GW170817 in evening twilight at high airmass as the object was setting.

### 2018-03-07 chapter5/ms.tex
Add big photometry table to Ch 5
Clean up Table Styles
Consolidate acknoledgements

\section*{Abstract}
We present UV, optical, and NIR photometry of the first electromagnetic counterpart to a gravitational wave source from Advanced LIGO/Virgo, the binary neutron star merger GW170817. Our data set extends from the discovery of the optical counterpart at $0.47$ days to $18.5$ days post-merger, and includes observations with the Dark Energy Camera (DECam), Gemini-South/FLAMINGOS-2 (GS/F2), and the {\it Hubble Space Telescope} ({\it HST}). The spectral energy distribution (SED) inferred from this photometry at $0.6$ days is well described by a blackbody model with $T\approx 8300$ K, a radius of $R\approx 4.5\times 10^{14}$ cm (corresponding to an expansion velocity of $v\approx 0.3c$), and a bolometric luminosity of $L_{\rm bol}\approx 5\times10^{41}$ erg s$^{-1}$. At $1.5$ days we find a multi-component SED across the optical and NIR, and subsequently we observe rapid fading in the UV and blue optical bands and significant reddening of the optical/NIR colors. Modeling the entire data set we find that models with heating from radioactive decay of $^{56}$Ni, or those with only a single component of opacity from $r$-process elements, fail to capture the rapid optical decline and red optical/NIR colors. Instead, models with two components consistent with lanthanide-poor and lanthanide-rich ejecta provide a good fit to the data; the resulting ``blue'' component has $M_\mathrm{ej}^\mathrm{blue}\approx 0.01$ M$_\odot$ and $v_\mathrm{ej}^\mathrm{blue}\approx 0.3$c, and the ``red'' component has $M_\mathrm{ej}^\mathrm{red}\approx 0.04$ M$_\odot$ and $v_\mathrm{ej}^\mathrm{red}\approx 0.1$c. These ejecta masses are broadly consistent with the estimated $r$-process production rate required to explain the Milky Way $r$-process abundances, providing the first evidence that BNS mergers can be a dominant site of $r$-process enrichment.

@@

Here we present rapid-cadence UV, optical, and NIR observations spanning from the time of discovery to 18.5 days post-merger.  We construct well-sampled light curves and SEDs using data from DECam along with {\it Swift}, GS/F2, and {\it HST}. We show that the data cannot be fit by a model with heating from $^{56}$Ni radioactive decay and Fe-peak opacities (as in normal supernovae), but instead requires heating from $r$-process nuclei and at least two components consistent with lanthanide-poor and lanthanide-rich opacities. We further use the data to determine the ejecta masses and velocities for each component.

@@

\subsection{Swift/UVOT}
\label{sec:ch5_data_UVOT}
The UVOT instrument on-board {\it Swift} \citep{Gehrels+04, Roming+05} began observing the field of the optical counterpart on 2017 August 18.167 UT with the {\it U}, {\it W1}, {\it W2}, and {\it M2} filters \citep{Evans+17}.  We use the latest {\tt HEAsoft} release (v6.22) with the corresponding calibration files and updated zero-points to independently analyze the data. We perform photometry in a $3\arcsec$ photometric aperture to minimize the contamination from host galaxy light, following the prescriptions by \citet{Brown+09}. We estimate and subtract the contribution from host galaxy light using deep UVOT observations acquired at later times, when the UV emission from the transient was no longer present in the images (\swift ID 07012979003). The systematic effect from the host light contamination is $\approx 3\%$ (see e.g., \citealt{Brown+09}).

@@

We find a similar rapid evolution in the colors of the transient (\Cref{fig:ch5_sed}).  In particular, the $u-g$ and $g-r$ colors become redder by about 1 mag between about 1.5 and 3.5 days.  The colors in the redder optical bands exhibit slower evolution, with $r-i\approx 0.5-1$ mag, $i-z\approx 0-0.5$ mag, and $z-Y\approx 0.3$ mag.  These colors are significantly redder than those of known supernovae near explosion (e.g., \citealt{folatelli2009,bianco2014,galbany2016}).

@@

>>>>

\section*{Abstract}
We present UV, optical, and NIR photometry of the first electromagnetic counterpart to a gravitational wave source from Advanced LIGO/Virgo, the binary neutron star merger GW170817. Our data set extends from the discovery of the optical counterpart at $0.47$ days to $18.5$ days post-merger, and includes observations with the Dark Energy Camera (DECam), Gemini-South/FLAMINGOS-2 (GS/F2), and the {\it Hubble Space Telescope} (\HST). The spectral energy distribution (SED) inferred from this photometry at $0.6$ days is well described by a blackbody model with $T\approx 8300$ K, a radius of $R\approx 4.5\times 10^{14}$ cm (corresponding to an expansion velocity of $v\approx 0.3c$), and a bolometric luminosity of $L_{\rm bol}\approx 5\times10^{41}$ erg s$^{-1}$. At $1.5$ days we find a multi-component SED across the optical and NIR, and subsequently we observe rapid fading in the UV and blue optical bands and significant reddening of the optical/NIR colors. Modeling the entire data set we find that models with heating from radioactive decay of $^{56}$Ni, or those with only a single component of opacity from $r$-process elements, fail to capture the rapid optical decline and red optical/NIR colors. Instead, models with two components consistent with lanthanide-poor and lanthanide-rich ejecta provide a good fit to the data; the resulting ``blue'' component has $M_\mathrm{ej}^\mathrm{blue}\approx 0.01$ M$_\odot$ and $v_\mathrm{ej}^\mathrm{blue}\approx 0.3$c, and the ``red'' component has $M_\mathrm{ej}^\mathrm{red}\approx 0.04$ M$_\odot$ and $v_\mathrm{ej}^\mathrm{red}\approx 0.1$c. These ejecta masses are broadly consistent with the estimated $r$-process production rate required to explain the Milky Way $r$-process abundances, providing the first evidence that BNS mergers can be a dominant site of $r$-process enrichment.

@@

Here we present rapid-cadence UV, optical, and NIR observations spanning from the time of discovery to 18.5 days post-merger.  We construct well-sampled light curves and SEDs using data from DECam along with \swift, GS/F2, and \HST. We show that the data cannot be fit by a model with heating from $^{56}$Ni radioactive decay and Fe-peak opacities (as in normal supernovae), but instead requires heating from $r$-process nuclei and at least two components consistent with lanthanide-poor and lanthanide-rich opacities. We further use the data to determine the ejecta masses and velocities for each component.

@@

\subsection{Swift/UVOT}
\label{sec:ch5_data_UVOT}
The UVOT instrument on-board \swift \citep{Gehrels+04, Roming+05} began observing the field of the optical counterpart on 2017 August 18.167 UT with the {\it U}, {\it W1}, {\it W2}, and {\it M2} filters \citep{Evans+17}.  We use the latest {\tt HEAsoft} release (v6.22) with the corresponding calibration files and updated zero-points to independently analyze the data. We perform photometry in a $3\arcsec$ photometric aperture to minimize the contamination from host galaxy light, following the prescriptions by \citet{Brown+09}. We estimate and subtract the contribution from host galaxy light using deep UVOT observations acquired at later times, when the UV emission from the transient was no longer present in the images (\swift ID 07012979003). The systematic effect from the host light contamination is $\approx 3\%$ (see e.g., \citealt{Brown+09}).

@@

We find a similar rapid evolution in the colors of the transient (\Cref{fig:ch5_sed}).  In particular, the $u-g$ and $g-r$ colors become redder by about 1 mag between about 1.5 and 3.5 days.  The colors in the redder optical bands exhibit slower evolution, with $r-i\approx 0.5-1$ mag, $i-z\approx 0-0.5$ mag, and $z-Y\approx 0.3$ mag.  These colors are significantly redder than those of known supernovae near explosion (e.g., \citealt{Folatelli+10,Bianco+14,Galbany+16}).

@@

\section{Summary of Photometry}
\label{sec:ch5_photometry}

\singlespace
\begin{deluxetable}{lcccc}
\tabletypesize{\footnotesize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Summary of Photometry
	          \label{tab:ch5_phot}}
\tablehead{
\colhead{Telescope} &
\colhead{Instrument} &
\colhead{Filter} &
\colhead{MJD} &
\colhead{Mag [AB]}
}
\startdata
Blanco & DECam & $i$ & 0.4745 & $17.48 \pm 0.03$ \\
Blanco & DECam & $z$ & 0.4752 & $17.59 \pm 0.03$ \\
\swift & UVOT & $M2$ & 0.627 & $21.14 \pm 0.23$ \\
\swift & UVOT & $W1$ & 0.634 & $19.53 \pm 0.12$ \\
\swift & UVOT & $U$ & 0.639 & $18.20 \pm 0.09$ \\
\swift & UVOT & $W2$ & 0.643 & $20.76 \pm 0.20$ \\
\swift & UVOT & $U$ & 0.981 & $18.90 \pm 0.17$ \\
\swift & UVOT & $U$ & 1.043 & $18.98 \pm 0.16$ \\
Blanco & DECam & $Y$ & 1.4478 & $17.32 \pm 0.03$ \\
Blanco & DECam & $z$ & 1.4485 & $17.59 \pm 0.02$ \\
Blanco & DECam & $i$ & 1.4492 & $17.78 \pm 0.02$ \\
Blanco & DECam & $r$ & 1.4499 & $18.04 \pm 0.02$ \\
Blanco & DECam & $g$ & 1.4506 & $18.66 \pm 0.03$ \\
Blanco & DECam & $u$ & 1.4512 & $19.94 \pm 0.05$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 1.471 & $17.63 \pm 0.10$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 2.439 & $17.71 \pm 0.09$ \\
Blanco & DECam & $Y$ & 2.4461 & $17.77 \pm 0.03$ \\
Blanco & DECam & $z$ & 2.4472 & $18.18 \pm 0.03$ \\
Blanco & DECam & $i$ & 2.4479 & $18.38 \pm 0.03$ \\
Blanco & DECam & $r$ & 2.4486 & $19.03 \pm 0.03$ \\
Blanco & DECam & $g$ & 2.4492 & $20.21 \pm 0.05$ \\
Blanco & DECam & $u$ & 2.4515 & $22.26 \pm 0.16$ \\
Blanco & DECam & $Y$ & 3.4541 & $18.05 \pm 0.03$ \\
Blanco & DECam & $z$ & 3.4551 & $18.56 \pm 0.03$ \\
Blanco & DECam & $u$ & 3.4556 & $23.06 \pm 0.32$ \\
Blanco & DECam & $i$ & 3.4558 & $18.73 \pm 0.03$ \\
Blanco & DECam & $r$ & 3.4564 & $19.29 \pm 0.04$ \\
Blanco & DECam & $g$ & 3.4571 & $20.93 \pm 0.08$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 4.445 & $17.92 \pm 0.10$ \\
Blanco & DECam & $Y$ & 4.4467 & $18.35 \pm 0.03$ \\
Blanco & DECam & $z$ & 4.4491 & $18.81 \pm 0.03$ \\
Blanco & DECam & $i$ & 4.4516 & $19.22 \pm 0.03$ \\
Blanco & DECam & $r$ & 4.4552 & $20.25 \pm 0.05$ \\
Blanco & DECam & $g$ & 4.4624 & $21.73 \pm 0.11$ \\
Blanco & DECam & $Y$ & 5.4460 & $18.83 \pm 0.18$ \\
Blanco & DECam & $z$ & 5.4484 & $19.17 \pm 0.11$ \\
Blanco & DECam & $i$ & 5.4508 & $19.55 \pm 0.18$ \\
Blanco & DECam & $r$ & 5.4545 & $20.79 \pm 0.24$ \\
Blanco & DECam & $g$ & 5.462 & $>20.80$ \\
Blanco & DECam & $Y$ & 6.4458 & $19.06 \pm 0.31$ \\
Blanco & DECam & $r$ & 6.457 & $>19.60$ \\
Blanco & DECam & $g$ & 6.468 & $>20.67$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 7.438 & $18.79 \pm 0.14$ \\
Blanco & DECam & $Y$ & 7.4448 & $19.44 \pm 0.05$ \\
Blanco & DECam & $z$ & 7.4509 & $19.89 \pm 0.05$ \\
Blanco & DECam & $i$ & 7.4533 & $20.54 \pm 0.05$ \\
Blanco & DECam & $r$ & 7.4581 & $21.23 \pm 0.11$ \\
Blanco & DECam & $g$ & 7.469 & $>22.19$ \\
Blanco & DECam & $Y$ & 8.4446 & $20.06 \pm 0.07$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 8.452 & $19.22 \pm 0.18$ \\
Blanco & DECam & $z$ & 8.4543 & $20.40 \pm 0.06$ \\
Blanco & DECam & $i$ & 8.4591 & $20.72 \pm 0.06$ \\
Blanco & DECam & $r$ & 8.4688 & $21.95 \pm 0.18$ \\
Blanco & DECam & $Y$ & 9.4457 & $20.78 \pm 0.11$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 9.449 & $19.62 \pm 0.15$ \\
Blanco & DECam & $z$ & 9.4659 & $21.19 \pm 0.07$ \\
Blanco & DECam & $i$ & 9.4712 & $21.37 \pm 0.06$ \\
\HST & WFC3/IR & F110W & 9.753 & $20.57 \pm 0.04$ \\
\HST & WFC3/IR & F160W & 9.768 & $19.89 \pm 0.04$ \\
\HST & WFC3/UVIS & F336W & 9.819 & $26.92 \pm 0.27$ \\
\HST & ACS/WFC & F475W & 9.905 & $23.95 \pm 0.06$ \\
\HST & ACS/WFC  & F625W & 9.969 & $22.88 \pm 0.07$ \\
\HST & ACS/WFC  & F775W & 10.032 & $22.35 \pm 0.08$ \\
\HST & ACS/WFC  & F850LP & 10.045 & $21.53 \pm 0.05$ \\
Blanco & DECam & $Y$ & 10.4462 & $21.67 \pm 0.21$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 10.449 & $18.43 \pm 0.25$ \\
Gemini-South & FLAMINGOS-2 & $H$ & 10.453 & $20.04 \pm 0.15$ \\
Blanco & DECam & $z$ & 10.4583 & $22.06 \pm 0.13$ \\
Blanco & DECam & $i$ & 10.4715 & $22.38 \pm 0.10$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 11.455 & $19.03 \pm 0.17$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 12.447 & $19.42 \pm 0.16$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 13.441 & $19.63 \pm 0.23$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 14.446 & $19.90 \pm 0.21$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 15.447 & $20.13 \pm 0.25$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 16.446 & $20.43 \pm 0.30$ \\
Gemini-South & FLAMINGOS-2 & $K_s$ & 18.450 & $20.84 \pm 0.26$ \\
\enddata
\tablecomments{Summary of photometry from \cref{sec:ch2_observations}. Dates are give in days relative to the time of the GW trigger (MJD = 57982.529). Photometry {\it is not} corrected for extinction. Limits are given at the $3\sigma$ level. Error bars are given at the $1\sigma$ level.}
\end{deluxetable}
